State-space analysis of continuous gravitational waves with a pulsar timing array: inclusion of the pulsar terms

### 2023-11-27 manuscript/manuscript_2/paper.tex
PP plot for large npoints

			\vspace{1mm} &  $\chi^{(n)}$       &$\Omega \left( 1 + \boldsymbol{n}\cdot \boldsymbol{q}^{(n)} \right)  d_{\rm ATNF}^{(n)} $  & rad & Uniform($0, 2 \pi $) \\

@@

\subsection{Parameter estimation} \label{sec:pe_and_ms} 
In this section, we apply the Kalman filter in conjunction with nested sampling to calculate the joint posterior probability distribution $p({\boldsymbol{\theta'}} | {\boldsymbol{Y}})$ for synthetic data $\boldsymbol{Y}$, and compare it to the known, injected values. The procedure is undertaken for multiple realisations of the noise processes $\xi^{(n)}(t)$ and $\varepsilon^{(n)}(t)$. That is, given the injected static parameters $\boldsymbol{\theta'}$, multiple realisations of $\boldsymbol{Y}$ are generated using the methods described in Section \ref{sec:synthetic_data}, and for each realisation we independently estimate $\boldsymbol{\theta'}$. The aims are (i) to demonstrate that the analysis scheme works (i.e.\ that it converges to a well-behaved, unimodal posterior for multiple noise realisations), (ii) to give a preliminary sense of its accuracy, and (iii) quantify the natural random dispersion in the one-dimensional posterior medians between noise realisations. The injected static GW source parameters $\boldsymbol{\theta}_{\rm gw}$ used for this mock analysis to generate $\boldsymbol{Y}$ are selected to be astrophysically reasonable and representative. Different values of the static GW source parameters are explored in Section \ref{sec:parameter_space}. The static pulsar parameters $\boldsymbol{\theta'}_{\rm psr}$  are as specified in Section \ref{sec:synthetic_data}. All injected static parameters $\boldsymbol{\theta}'$ are summarised in the second column of Table \ref{tab:parameters_and_priors}. The specification of the priors on $\boldsymbol{\theta'}$ is described in Appendix \ref{sec:set_priors} and summarised in the rightmost column of Table \ref{tab:parameters_and_priors}. \newline

Figure \ref{fig:corner_plot_1} displays results for the seven parameters in $\boldsymbol{\theta}_{\rm gw}$ for 10 arbitrary noise realisations in the form of a traditional corner plot. The histograms are the one-dimensional posteriors for each parameter, marginalized over the six other parameters. Each coloured curve is the result for different noise realisation. The solid orange line marks the known injected value. The two-dimensional contours mark the (0.5, 1, 1.5, 2)-sigma level surfaces. All histograms and contours are consistent with a unimodal joint posterior, which peaks near the known, injected values. There is scant evidence of railing against the prior bounds. There is no strong evidence for correlations between parameter pairs, e.g.\ banana-shaped contours. The injected value is contained within the 90\% credible interval of the one-dimensional marginalized posteriors in \textcolor{red}{YY} (i.e. \textcolor{red}{YY} $\%$) out of the \textcolor{red}{YY} possible combinations of the seven parameters and \textcolor{red}{YY} realizations. For this representative example, with characteristic strain \textcolor{red}{XX} the analysis scheme estimates $\boldsymbol{\theta}_{\rm gw}$ accurately. \newline

In addition to estimates of $\boldsymbol{\theta}_{\rm gw}$, it is of interest how well the pulsar-term phase correction parameters $\chi^{(n)}$ can be estimated, since this parameter is a key feature of our approach. Figure \ref{fig:corner_plot_3} displays the results for a representative subset of five parameters of $\chi^{(n)}$, $ \{\chi^{(1)} \dots \chi^{(5)} \}$ over \textcolor{red}{YY} noise realisations, analogously to Figure \ref{fig:corner_plot_1}. We do not display the resulting corner plot for all elements of $\chi^{(n)}$ because it is too big. All elements of $\chi^{(n)}$ are recovered unambiguously across all noise realisations, with the injected value contained within the 90\% credible interval of the one-dimensional marginalized posteriors in \textcolor{red}{YY} (i.e. \textcolor{red}{YY} $\%$) out of the \textcolor{red}{YY} possible combinations of the seven parameters and \textcolor{red}{YY} realizations. Similar results are obtained for the remaining 4$N$ parameters of $\boldsymbol{\theta}_{\rm psr}'$; the parameters are recovered unambiguously across the \textcolor{red}{XX} noise realisations. For the sake of brevity we do not display the calculated posterior distributions here because the inference of $\boldsymbol{\theta}_{\rm gw}$ is the main focus of this paper and PTA analyses. \newline

Figure \ref{fig:corner_plot_1} confirms two points: (i) the analysis scheme returns accurate answers for arbitrary noise realisations and (ii) there is appreciable natural random dispersion in the one-dimensional posterior medians between noise realisations. Regarding the second point, quantifying the dispersion is important since it is a practical measure of the accuracy of the parameter estimation scheme when it is applied to real astronomical data, where the true parameter values and specific noise realisations are unknown. \newline

% stacked_GW_plot_small_h_definitive2
\begin{figure*}
	\includegraphics[width=\textwidth, height =\textwidth ]{images/corner_lowSNR}
	\caption{Posterior distribution of the GW source parameters $\boldsymbol{\theta}_{\rm gw}$ for the representative system in Table \ref{tab:parameters_and_priors}, for nine realisations of the noise processes, with curves coloured uniquely. The horizontal and vertical orange lines indicate the true injected values. The contours in the two-dimensional histograms mark the (0.5, 1, 1.5, 2)-$\sigma$ levels after marginalizing over all but two parameters. The one-dimensional histograms correspond to the joint posterior distribution marginalized over all but one parameter. The supertitles of the one-dimensional histograms record the posterior median and the 0.16 and 0.84 quantiles of the median realisation. We plot the scaled variables $10^9 \Omega$ (units: ${\rm rad \, s^{-1}}$) and $10^{15} h_0$. The Kalman filter and nested sampler estimate accurately all seven parameters in ${\boldsymbol{\theta}}_{\rm gw}$. The horizontal axes span a subset of the prior domain for all seven parameters. The known, injected value lies within the 90\% credible interval for \textcolor{red}{X} out of the 63 combinations of seven parameters and nine noise realizations. There is an appreciable dispersion among the peaks of the one-dimensional posteriors, with coefficient of variation \textcolor{red}{X} across the 63 combinations.}
	\label{fig:corner_plot_1}
\end{figure*}

%images/corner_lowSNR_chiF
	\begin{figure}
	\includegraphics[width=\columnwidth, height =\columnwidth ]{images/corner_lowSNR_chi}
	\caption{Same as Figure \ref{fig:corner_plot_1}	but for 5 static parameters of $\chi^{(n)}$. The known, injected value lies within the 90\% credible interval for \textcolor{red}{X} out of the \textcolor{red}{X} combinations of five parameters and v\textcolor{red}{X} noise realizations. }
	\label{fig:corner_plot_3}
\end{figure}

\subsection{Extension to broader parameter space} \label{sec:parameter_space}
%images/pp_plot_new1
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{example-image-c}
	\caption{Fraction of injections included within a given credible interval of the estimated posterior, as a function of the credible interval itself (i.e. PP plot). The injections are 200 simulated GW sources generated by drawing randomly five parameters in $\boldsymbol{\theta}_{\rm gw}$ from the prior distributions in Table \ref{tab:parameters_and_priors}. Each coloured curve corresponds to a different parameter (see legend). The parameters $h_0$ and $\iota$ are fixed at $5 \times 10^{-15}$ and 1.0 rad respectively in order to maintain an approximately constant SNR. The grey shaded contours label the $1\sigma$, $2\sigma$ and 3$\sigma$ confidence intervals. For parameters with well estimated posteriors, the PP curve should fall along the diagonal of unit slope. $\Omega$ is generally well-estimated (i.e. it lies close to the unit diagonal) but the four other parameters show evidence of being over-constrained (i.e. the curves lie above the unit diagonal for low credible intervals, and below the unit diagonal for high credible intervals). This is due to a modelling bias whose origin is discussed in Sections \ref{sec:parameter_estim} and \ref{sec:pulsar_terms_drop}.}
	\label{fig:parameter_space}
\end{figure}
Section \ref{sec:pe_and_ms} focuses on a single representative system, parameterised in Table \ref{tab:parameters_and_priors}. In this section we test the method for various systems, varying the SMBHB source parameters $\boldsymbol{\theta}_{\rm gw}$ through astrophysically relevant ranges. The aim of this section is to confirm that the analysis scheme can be applied across an astrophysically relevant parameter space and that the arbitrary choice of $\boldsymbol{\theta}_{\rm gw}$ in Section \ref{sec:pe_and_ms} is not particularly advantageous by accident. \newline

We analyse \textcolor{red}{X} injections constructed by fixing $h_0 =$ \textcolor{red}{Y}  and $\iota =1.0$ rad and drawing the remaining five elements of $\boldsymbol{\theta}_{\rm gw}$ randomly from the prior distributions defined in Table \ref{tab:parameters_and_priors}. We fix $h_0$ and $\iota$ in order to maintain an approximately constant signal-to-noise ratio (SNR) across the  \textcolor{red}{X} injections. For each injection we compute the posterior distribution of ${\boldsymbol{\theta}}_{\rm gw}$. \newline

The results are displayed in Figure \ref{fig:parameter_space}. Since it is prohibitive to produce corner plots analogous to Figure \ref{fig:corner_plot_1} for \textcolor{red}{X} injections, in order to summarise the results we use a parameter-parameter (PP) plot \citep{doi:10.1198/106186006X136976}. A PP plot displays the fraction of injections included within a given credible interval of the estimated posterior, as a function of the credible interval itself. In the ideal case of perfect recovery, the PP plot should be a diagonal line of unit slope.  In Figure \ref{fig:parameter_space} the shaded grey contours enclose the $1\sigma$, $2\sigma$, and $3\sigma$ significance levels for \textcolor{red}{X} injections. We see that... \textcolor{red}{TBD once simulations complete}

\textcolor{red}{TK: there is an obvious additional feature that I haven't yet mentioned in the text, which is the systematic offset in iota and h w.r.t the injection. I think this is likely a sampler setting. I am currently running some checks, and will then add few sentences discussing this, or update the results/plots.}

@@

The results for the seven parameters of  $\boldsymbol{\theta}_{\rm gw}$ are shown in Figure \ref{fig:corner_plot_compare_high} for the high-SNR system and in Figure \ref{fig:corner_plot_compare_low} for the low-SNR system. The corner plot is arranged identically to Figure \ref{fig:corner_plot_1}, however the different coloured curved now correspond to different inference models, rather than different realisations of $\boldsymbol{Y}$. The blue curves are the results derived using $\mathcal{M}_{E}$. The green curves are the results derived using $\mathcal{M}_{\rm P \& E}$. \newline

@@

	\begin{figure*}
	\includegraphics[width=\textwidth, height =\textwidth ]{images/corner_highSNR_compare}
	\caption{Posterior distribution of the GW source parameters $\boldsymbol{\theta}_{\rm gw}$ for the representative system described in Table \ref{tab:parameters_and_priors}, with $h_0 = 10^{-12}$, for a single realisation of the system noise. The blue curves are the posteriors derived using the Earth-term model, Equation \eqref{eq:g_func_trig_earth}, the green curves using the pulsar-term model, Equation \eqref{eq:g_func_trig}. The vertical orange lines indicate the true injected values. The contours in the 2D histograms denote the (0.5, 1, 1.5, 2)-$\sigma$ levels. We plot the scaled variables $10^9 \Omega$ (units: rad s$^{-1}$) and $10^{15} h_0$. Some parameters (e.g. $\psi, \iota$) exhibit a bias when using the Earth-term model which is absent when using the pulsar-term model. \textcolor{red}{TK: need to remove these subtitles and correct the labels for omega and h. The actual results here may also be updated (same for Figure 5)}}
	\label{fig:corner_plot_compare_high}
\end{figure*}

@@

>>>>

			\vspace{1mm} &  $\chi^{(n)}$       &$\Omega \left( 1 + \boldsymbol{n}\cdot \boldsymbol{q}^{(n)_{\rm ATNF}} \right)  d_{\rm ATNF}^{(n)} $  & rad & Uniform($0, 2 \pi $) \\

@@

\subsection{Parameter estimation} \label{sec:pe_and_ms} 
In this section, we apply the Kalman filter in conjunction with nested sampling to calculate the joint posterior probability distribution $p({\boldsymbol{\theta'}} | {\boldsymbol{Y}})$ for synthetic data $\boldsymbol{Y}$, and compare it to the known, injected values. The procedure is undertaken for multiple realisations of the noise processes $\xi^{(n)}(t)$ and $\varepsilon^{(n)}(t)$. That is, given the injected static parameters $\boldsymbol{\theta'}$, multiple realisations of $\boldsymbol{Y}$ are generated using the methods described in Section \ref{sec:synthetic_data}, and for each realisation we independently estimate $\boldsymbol{\theta'}$. The aims are (i) to demonstrate that the analysis scheme works (i.e.\ that it converges to a well-behaved, unimodal posterior for multiple noise realisations), (ii) to give a preliminary sense of its accuracy, and (iii) quantify the natural random dispersion in the one-dimensional posterior medians between noise realisations. 
Regarding point (iii), quantifying the dispersion is important since it is a practical measure of the accuracy of the parameter estimation scheme when it is applied to real astronomical data, where the true parameter values and specific noise realisations are unknown. The injected static GW source parameters $\boldsymbol{\theta}_{\rm gw}$ used for this mock analysis to generate $\boldsymbol{Y}$ are selected to be astrophysically reasonable and representative. Different values of the static GW source parameters are explored in Section \ref{sec:parameter_space}. The static pulsar parameters $\boldsymbol{\theta'}_{\rm psr}$  are as specified in Section \ref{sec:synthetic_data}. All injected static parameters $\boldsymbol{\theta}'$ are summarised in the second column of Table \ref{tab:parameters_and_priors}. The specification of the priors on $\boldsymbol{\theta'}$ is described in Appendix \ref{sec:set_priors} and summarised in the rightmost column of Table \ref{tab:parameters_and_priors}. \newline

Figure \ref{fig:corner_plot_1} displays results for the seven parameters in $\boldsymbol{\theta}_{\rm gw}$ for nine arbitrary noise realisations in the form of a traditional corner plot. The histograms are the one-dimensional posteriors for each parameter, marginalized over the six other parameters. Each coloured curve is the result for different noise realisation. The solid orange line marks the known injected value. The two-dimensional contours mark the (0.5, 1, 1.5, 2)-sigma level surfaces. All histograms and contours are consistent with a unimodal joint posterior, which peaks near the known, injected values. There is scant evidence of railing against the prior bounds. There is no strong evidence for correlations between parameter pairs, e.g.\ banana-shaped contours, although weak-correlations are evident between $\Omega$ and $\Phi_0$, $\psi$ and $\alpha$, and $\iota$ and $h_0$. The injected value is contained within the 90\% credible interval of the one-dimensional marginalized posteriors in 45 out of the 63 possible combinations of the seven parameters and 63 realizations (i.e. 70 $\%$). There is appreciable natural random dispersion in the one-dimensional posterior medians between noise realisations. The minimum coefficient of variation is obtained for $\Omega$ at  0.2 \%, the maximum value is obtained for $\Phi_0$ at 43 \%. The remaining parameters have typical values $\lessapprox 10 \%$. For this representative example, with characteristic strain $h_0 = 5 \times 10^{-15}$ the analysis scheme estimates $\boldsymbol{\theta}_{\rm gw}$ accurately. Analogous results for synthetic data with higher strain ($h_0 = 10^{-12}$) are presented in Appendix \ref{sec:app_high_SNR} (Figure \ref{fig:corner_high_snr_appendix}). At higher strains the dispersion between noise realisations is reduced. \newline

In addition to estimates of $\boldsymbol{\theta}_{\rm gw}$, it is of interest how well the pulsar-term phase correction parameters $\chi^{(n)}$ can be estimated, since this parameter is a key feature of our approach. Figure \ref{fig:corner_plot_3} displays the results for a representative subset of five parameters of $\chi^{(n)}$, $ \{\chi^{(1)} \dots \chi^{(5)} \}$ over the nine noise realisations, analogously to Figure \ref{fig:corner_plot_1}. We do not display the resulting corner plot for all elements of $\chi^{(n)}$ because it is too big. With the exception of the results for $\chi^{(2)}$ (discussed below), all histograms and contours are consistent with a unimodal joint posterior, which peaks near the known, injected values. There is no evidence for correlations between parameter pairs. The majority of the elements of $\chi^{(n)}$ are recovered unambiguously across all noise realisations; for the 47 elements of $\chi^{n}$ (i.e. not just the five elements plotted in Figure \ref{fig:corner_plot_3}), the injected value is  contained within the 90\% credible interval of the one-dimensional marginalized posteriors in 325 out of the 423 possible combinations of the 47 parameters and nine realizations (i.e. $\sim$ 77 $\%$). There are some elements for which consistent estimates are not obtained across multiple realisations, e.g $\chi^{(2)}$, (third row, third column of Figure \ref{fig:corner_plot_3}). This corresponds to the phase-correction term for PSR J0340+4130. This pulsar lies in the closest direction to our synthetic gw source, such that $| \boldsymbol{n} \cdot \boldsymbol{q}^{(2)}| = 0.96$. As a result the magnitude of $\cos \left( \chi^{(2)}\right) \sim 0.07$, and the influence of the pulsar term is minimal. The inability to accurately infer $\chi^{(2)}$ is contingent on the magnitude of the GW signal relative to the measurement noise; for synthetic data with $h_0 = 10^{-12}$, $\chi^{(2)}$ can be recovered accurately, see Figure \ref{fig:corner_high_snr_appendix_chi} in Appendix \ref{sec:app_high_SNR}. \newline

Similar results are obtained for the remaining 4$N$ parameters of $\boldsymbol{\theta}_{\rm psr}'$; the injected values are recovered unambiguously across the nine noise realisations. For the sake of brevity we do not display the calculated posterior distributions here because the inference of $\boldsymbol{\theta}_{\rm gw}$ is the main focus of this paper and PTA analyses. \newline

 \textcolor{red}{TK: there is an obvious additional feature that I haven't yet mentioned in the text, which is the systematic offset in iota and h w.r.t the injection. The systematic-ness makes me think this is likely a sampler setting. I am currently running some checks, and will then add few sentences discussing this, or update the results/plots.}

\begin{figure*}
	\includegraphics[width=\textwidth, height =\textwidth ]{images/corner_lowSNR}
	\caption{Posterior distribution of the GW source parameters $\boldsymbol{\theta}_{\rm gw}$ for the representative system in Table \ref{tab:parameters_and_priors}, for nine realisations of the noise processes, with curves coloured uniquely. The horizontal and vertical orange lines indicate the true injected values. The contours in the two-dimensional histograms mark the (0.5, 1, 1.5, 2)-$\sigma$ levels after marginalizing over all but two parameters. The one-dimensional histograms correspond to the joint posterior distribution marginalized over all but one parameter. The supertitles of the one-dimensional histograms record the posterior median and the 0.16 and 0.84 quantiles of the median realisation. We plot the scaled variables $10^9 \Omega$ (units: ${\rm rad \, s^{-1}}$) and $10^{15} h_0$. The Kalman filter and nested sampler estimate accurately all seven parameters in ${\boldsymbol{\theta}}_{\rm gw}$. The horizontal axes span a subset of the prior domain for all seven parameters. The known, injected value lies within the 90\% credible interval for 45 out of the 63 combinations of seven parameters and nine noise realizations. There is an appreciable dispersion among the peaks of the one-dimensional posteriors; the maximum coefficient of variation is $43 \%$ for $\Phi_0$, the minimum is $0.02 \%$ for $\Omega$.}
	\label{fig:corner_plot_1}
\end{figure*}

%images/corner_lowSNR_chiF
	\begin{figure}
	\includegraphics[width=\columnwidth, height =\columnwidth ]{images/corner_lowSNR_chi}
	\caption{Same as Figure \ref{fig:corner_plot_1}	but for five static parameters of $\chi^{(n)}$. Consistent unimodal posteriors are obtained across the nine noise realisations for four out of the five displayed parameters. No consistent posteriors are obtained for $\chi^{(2)}$ (third row, third column), because this pulsar has a similar sky position to that of the synthetic GW source. The known, injected value lies within the 90\% credible interval for 37 out of the 45 combinations of five parameters and nine noise realizations (i.e. $82 \%$). }
	\label{fig:corner_plot_3}
\end{figure}

\subsection{Extension to broader parameter space} \label{sec:parameter_space}
%images/pp_plot_new1
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{images/pp_plot_canonical500}
	\caption{Fraction of injections included within a given credible interval of the estimated posterior, as a function of the credible interval itself (i.e. PP plot). The injections are 200 simulated GW sources generated by drawing randomly five parameters in $\boldsymbol{\theta}_{\rm gw}$ from the prior distributions in Table \ref{tab:parameters_and_priors}. Each coloured curve corresponds to a different parameter (see legend). The parameters $h_0$ and $\iota$ are fixed at $5 \times 10^{-15}$ and 1.0 rad respectively in order to maintain an approximately constant SNR. The grey shaded contours label the $1\sigma$, $2\sigma$ and 3$\sigma$ confidence intervals. For parameters with well estimated posteriors, the PP curve should fall along the diagonal of unit slope. $\Omega$ and $\alpha$ are generally well-estimated (i.e. the curves lie close to the unit diagonal). The remaining three parameters, $\psi$, $\phi_0$ and $\delta$ show modest evidence of being over-constrained and stray outside the shaded region.}
	\label{fig:parameter_space}
\end{figure}
Section \ref{sec:pe_and_ms} focuses on a single representative system, summarised in Table \ref{tab:parameters_and_priors}. In this section we test the method for various systems, varying the SMBHB source parameters $\boldsymbol{\theta}_{\rm gw}$ through astrophysically relevant ranges. The aim of this section is to confirm that the analysis scheme can be applied across an astrophysically relevant parameter space and that the arbitrary choice of $\boldsymbol{\theta}_{\rm gw}$ in Section \ref{sec:pe_and_ms} is not particularly advantageous by accident. \newline

We analyse 200 injections constructed by fixing $h_0 = 5 \times 10^{-15}$, $\iota =1.0$ rad and drawing the remaining five elements of $\boldsymbol{\theta}_{\rm gw}$ randomly from the prior distributions defined in Table \ref{tab:parameters_and_priors}. We fix $h_0$ and $\iota$ in order to maintain an approximately constant signal-to-noise ratio (SNR) across the 200 injections. For each injection we compute the posterior distribution of ${\boldsymbol{\theta}}_{\rm gw}$. The static pulsar parameters $\boldsymbol{\theta'}_{\rm psr}$ are as specified in Section \ref{sec:synthetic_data} and Table  \ref{tab:parameters_and_priors}. \newline

It is prohibitive to produce corner plots analogous to Figure \ref{fig:corner_plot_1} for 200 injections and seven elements of $\boldsymbol{\theta}_{\rm gw}$. Therefore, in order to summarise the results we use a parameter-parameter (PP) plot \citep{doi:10.1198/106186006X136976}. A PP plot displays the fraction of injections included within a given credible interval of the estimated posterior, as a function of the credible interval itself. In the ideal case of perfect recovery, the PP plot should be a diagonal line of unit slope.

The results are displayed in Figure \ref{fig:parameter_space}.  
The shaded grey contours enclose the $1\sigma$, $2\sigma$, and $3\sigma$ significance levels for 200 injections. The curves for the five parameters generally exhibit the discussed linear behaviour.

Some parameters are consistently well estimated across the parameter space; the blue curve for $\Omega$ is consistently contained within the 2-$\sigma$ shaded region.

Conversely some parameters e.g. $\psi$ stray outside the $1\sigma$ bounded region and show evidence of being over constrained; there are more injections contained within lower-value credible intervals than would be expected statistically, and more injections contained within higher-value credible intervals.

\textcolor{red}{TK: can we do better than this?}

The

At this signal-to-noise ratio

the polarisation angle does stray above /below

At lowe SNR the ability to resolve the depends upon the noise realisation and the source location. The antenna pattern function formed by the NANOGrav 12.5 year pulsars is sensitive to different parts of the sky. Areas with lower sensitivity may need to be

Conversely the ability to infer $\Omega$ depends less on sky position or values.

@@

The results for the seven parameters of  $\boldsymbol{\theta}_{\rm gw}$ are shown in Figure \ref{fig:corner_plot_compare_high} for the high-SNR system and in Figure \ref{fig:corner_plot_compare_low} for the low-SNR system. The corner plot is arranged identically to Figure \ref{fig:corner_plot_1}, however the different coloured curved now correspond to different inference models, rather than different realisations of $\boldsymbol{Y}$. The blue curves are the results derived using $\mathcal{M}_{\rm E}$. The green curves are the results derived using $\mathcal{M}_{\rm P \& E}$. \newline

@@

	\begin{figure*}
	\includegraphics[width=\textwidth, height =\textwidth ]{images/corner_highSNR_compare}
	\caption{Posterior distribution of the GW source parameters $\boldsymbol{\theta}_{\rm gw}$ for the representative system described in Table \ref{tab:parameters_and_priors}, with $h_0 = 10^{-12}$, for a single realisation of the system noise. The blue curves are the posteriors derived using the Earth-term model, Equation \eqref{eq:g_func_trig_earth}, the green curves using the pulsar-term model, Equation \eqref{eq:g_func_trig}. The vertical orange lines indicate the true injected values. The contours in the 2D histograms denote the (0.5, 1, 1.5, 2)-$\sigma$ levels. The supertitles of the one-dimensional histograms record the posterior medians and the 0.16 and 0.84 quantiles of the green curves, i.e. the pulsar-term model. We plot the scaled variables $10^9 \Omega$ (units: rad s$^{-1}$) and $10^{12} h_0$. Some parameters (e.g. $\psi, \iota$) exhibit a bias when using the Earth-term model which is absent when using the pulsar-term model.}
	\label{fig:corner_plot_compare_high}
\end{figure*}

@@

\section{Canonical example, high SNR} \label{sec:app_high_SNR}

		\begin{figure}
	\includegraphics[width=\columnwidth, height = \columnwidth ]{example-image-a} 	
	\caption{}
	\label{fig:corner_high_snr_appendix}
\end{figure}

	\begin{figure}
	\includegraphics[width=\columnwidth, height = \columnwidth ]{example-image-b} 	
	\caption{}
	\label{fig:corner_high_snr_appendix_chi}
\end{figure}
